\documentclass[letterpaper,12pt]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{fullpage}
\usepackage{setspace}

\title{Team 6 Challenge Proposal}
\author{6.141\\
	Spring 2012\\ \\
	Neil Forrester\\
	Dan Gonzalez\\
	Raghavendra Srinivasan\\
	James Wiken}

\onehalfspacing				

\begin{document}
\begin{singlespacing}
\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\listoffigures
\listoftables
\thispagestyle{empty}
\newpage

\end{singlespacing}

\setcounter{page}{1}

\section{Problem Statement}
The scenario we wish to emulate can be pictured as a robot being parachuted onto the surface of Mars with the purpose of building a shelter of some form.  Building materials have also been parachuted down and are distributed across the Martian landscape.  The robot has been provided with a map of the local area and the locations of some of the building materials.  However, some of the materials have not landed in the designated areas and thus do not show up on the map despite being useful, or perhaps essential, to the construction of the shelter.  The robot must navigate the countryside, gather materials, and use said materials to build a structure.

Similarly, our robot must perform four main tasks.  

\begin{enumerate}
 \item {\bf Navigate about an area}: The robot will be placed in a maze of some undefined size and complexity.  The robot will be provided a map of the maze beforehand and must be able to autonomously navigate the area.
 \item {\bf Locate and collect building materials}: Building materials in the form of differently colored blocks will be placed around the area.  Locations of some of the blocks will be provided with the map, but some subset of the blocks are not marked on the map.  The robot must be able to locate, recognize, and collect some subset of the blocks.
 \item {\bf Transport building materials to construction zone}: The robot must be able to move the collected blocks from their initial positions to an autonomously determined construction point.
 \item {\bf Assemble materials into a structure}: Using the collected building materials, the robot must build a structure.  The structure is roughly defined as a collection of blocks within the construction zone.  The structure can range from simple, such as a pile or a low wall, to complex, such as an enclosed room or an archway.  
\end{enumerate}

The integration of these four different abilities into a single task makes this project both interesting and challenging.  The elements needed to solve this problem can be used to further other robot applications like those listed above.  Conversely, other applications can provide at least partial solutions to this problem. 

Before proceeding with the design of a solution to the given problem statement, a series of assumptions must be made.  These assumptions can be divided into three main categories: assumptions about the environment, assumptions about the building blocks, and assumptions about the robot.

\subsection{Assumptions about the environment}
%TODO: text here

\subsection{Assumptions about the building blocks}
%TODO: text here

\subsection{Assumptions about the robot}
%TODO: text here


\section{High level approach and mechanical structure}
The solution we've decided on has two primary modes: collection and assembly.
In collection mode, the robot uses a funnel in front of the body to collect blocks (see figure ).
%TODO: figure reference here
The blocks are stored in a stack under the body.
The stack is sufficently narrow so that the blocks will interlock.
To guard against blocks getting stuck in the funnel,
there will be a break-beam sensor in the throat (not illustrated).
If a block gets stuck, the robot will back up, turn slightly, and approach the block again.

After collecting a sufficent number of blocks in the stack, the robot will back up.
This will deposit the blocks in a straight line in front of the robot, and aligned with the robot center.
Now the robot will use the robotic arm to rearrange the blocks into an arbitrary planar structure.
This will be precise and efficent, because the robot will not have to turn at all to place the blocks,
and visual feedback can be used to check block placement.

\section{Systems}
%TODO: do we want any text here?

\subsection{Master Controller}
The Master Controller is the brain of the system, does high-level planning, and decides when to stop.
High level operations will be broken down and handed out to other modules for execution.
%TODO: do we want to say anything more about this?

\subsection{Inventory and Mapping}
The Inventory and Mapping module provides the other modules with information about the environment.
This information includes the poses of blocks in the environment,
the blocks in the stack under the robot,
the walls of the maze,
the robot's current location,
and anything else we decide is useful.
The I\&M module takes input from the Perception module, and performs data fusion, mapping, and localization.
%TODO: do we want to say anything more about this?

\subsection{Navigation and Inverse Kinematics}
The Navigation and Inverse Kinematics module directly controls the robot's actuators.
Other modules give it commands such as ``travel to $(x, y, \theta)$'',
or ``Move the robotic arm gripper to $(x, y, z, \theta, \phi)$'',
and the N\&IK module will move the robot appropriately.
%TODO: do we want to say anything more about this?

\subsection{Manipulator}
The Manipulator takes commands from the Master Controller
and decides what motions need to be performed to manipulate the blocks.
For example, if the Master Controller commands ``collect block 42'',
the Manipulator will order the N\&IK module to make movements that will funnel the block into the stack.
%TODO: do we want to say anything more about this?

\subsection{Perception}
The Perception module reads data from the sensors and feeds information to the Inventory and Mapping module.
For example, if the camera image contains a hexagonal red blob,
the Perception module will interpret this as a block at an angle,
and report the presence of a block to the I\&M module.
%TODO: do we want to say anything more about this?

\section{Schedule}
%TODO: text here

\section{Conclusion}
%TODO: text here

\end{document}
